
%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
% 
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   

\documentclass{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
 
% \usepackage{geometry}
% %\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
% 
% \usepackage{xspace}
 
% \usepackage{epstopdf}
% \usepackage{graphicx,color}
% 
% 
\usepackage{booktabs}
\usepackage{datatool}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usetikzlibrary{patterns}
\usepackage{lscape}
\usepackage{subfig}

\usepackage{url}
\urldef{\mailsa}\path|{alfred.hofmann, ursula.barth, ingrid.haas, frank.holzwarth,|
\urldef{\mailsb}\path|anna.kramer, leonie.kunz, christine.reiss, nicole.sator,|
\urldef{\mailsc}\path|erika.siebert-cole, peter.strasser, lncs}@springer.com|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Can Data Integration Quality be Enhanced on Multi-cloud using SLA?}

% a short form should be given in case it is too long for the running head
%\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
% 
\author{
 Daniel A. S. Carvalho\inst{1},
 Pl\'acido A. Souza Neto\inst{3},  
        Genoveva Vargas-Solar\inst{4},
          Nadia Bennani\inst{2},
        Chirine Ghedira\inst{1}       
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Universit\'e Jean Moulin, Lyon 3 MAGELLAN, IAE -- France \\
			\email{daniel.carvalho@univ-lyon3.fr, chirine.ghedira-guegan@univ-lyon3.fr}
		\and
		CNRS INSA-Lyon, LIRIS, UMR5205 -- France\\
			\email{nadia.bennani@insa-lyon.fr}
		\and
		Instituto Federal do Rio Grande do Norte, Natal -- Brazil \\
			\email{placido.neto@ifrn.edu.br}
		\and
		CNRS, LIG-LAFMIA, Saint Martin d'H\`eres -- France \\
			\email{genoveva.vargas@imag.fr}
		}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\maketitle

 
% \begin{abstract}
% The abstract should summarize the contents of the paper and should
% contain at least 70 and at most 150 words. It should be written using the
% \emph{abstract} environment.
% 
% \keywords{We would like to encourage you to list your keywords within
% the abstract section}
% \end{abstract}


%\input{Title-And-Authors}

\input{Abstract-And-Keywords}

% -------------------------------- Introduction -------------------------------- %
\section{Introduction}
\label{sec:intro}
\input{intro} 
% --------------------------------              -------------------------------- %
 
%. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 
\section{Data integration challenges: classification scheme}\label{sec:sm}
%. . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . . 
\input{section-3} % Mapping Process %
% --------------------------------              -------------------------------- %

%\input{section-4} % Quantitative Analysis %
% --------------------------------              -------------------------------- %

%-[BEGIN]-----------------------------------------------------------------------
%\section{Enhancing  Data Integration on Multi-Cloud environments with SLA}\label{sec:approach}
%-[END]-----------------------------------------------------------------------
%\input{section-5} % Approach ... %

% -------------------------------- Related Works ------------------------------- %
%\section{Related Works}\label{sec:rw}
%\input{section-2}
% --------------------------------              -------------------------------- %

%\section{Infrastructure implemented for the scenario}

\section{Conclusion and final remarks}\label{sec:conc}
This paper introduces the challenge of integrating data from distributed data
services deployed on different cloud providers guided by service level
agreements (SLA) and user preferences statement. The data integration problem
is stated as a continuos data provision problem that has associated SLAs and
that uses techniques for ensuring different qualities of delivered data
(freshness, precision, completeness). The problem statement was derived from a
classification scheme that resulted from a study of existing publications
identified by applying the systematic mapping method. 
Our contribution is the definition of a classification scheme that shows the
aspects that characterize a modern vision of data integration done in
multi-cloud environments and that can be enhanced by including SLAs in its
process.  

Current big data settings impose to consider SLA and different data delivery
models. We believe that given the volume and the complexity of query evaluation
that includes steps that imply greedy computations. It is important to combine
and revisit well-known solutions adapted to these contexts.

From the results of our systematic analysis, (i) we identified trends and open
issues in our research topic and proposed the general lines of an original data integration solution according to current
trends in the area; and (ii) we are also currently developing the strategies to
better define a SLA extension and data consumers preferences description for
guiding data integration in multi-cloud environments.
   
% We are currently developing the strategies and algorithms of our vision  applied
% to energy consumption applications and also to elections and political campaign data
% integration in order to guide decision making on campaign strategies.         

\bibliographystyle{plain}
\bibliography{bibliography,biblio,example}


\end{document}